---
title: "Modeling Runners"
author: "Eduardo Cantu Medellin, Samantha Sprague, Solange Garcia de Alford"
date: "September 19, 2019"
output: html_document
---

```{r setup}

library(XML)
ubase = "http://www.cherryblossom.org/"

### Set the menURL
menURLs = 
  c("results/1999/cb99m.html", #"cb99m.htm"
    "results/2000/Cb003m.htm", #"cb003m.htm"
    "results/2001/oof_m.html", #"results/2001/oof_m.html"
    "results/2002/oofm.htm", #"results/2002/oofm.htm"
    "results/2003/CB03-M.HTM", #"results/2003/CB03-M.HTM"
    "results/2004/men.htm", #"results/2004/men.htm"
    "results/2005/CB05-M.htm", #"results/2005/CB05-M.htm"
    "results/2006/men.htm", #"results/2006/men.htm"
    "results/2007/men.htm", #"results/2007/men.htm"
    "results/2008/men.htm", #"results/2008/men.htm"
    "results/2009/09cucb-M.htm", #"results/2009/09cucb-M.htm"
    "results/2010/2010cucb10m-m.htm", #"results/2010/2010cucb10m-m.htm"
    "results/2011/2011cucb10m-m.htm", #"results/2011/2011cucb10m-m.htm"
    "results/2012/2012cucb10m-m.htm" #"results/2012/2012cucb10m-m.htm"
    )

womenURLs = 
  c("results/1999/cb99f.html", #"cb99f.htm"
    "results/2000/Cb003f.htm", #"cb003m.htm"
    "results/2001/oof_f.html", #"results/2001/oof_m.html"
    "results/2002/ooff.htm", #"results/2002/oofm.htm"
    "results/2003/CB03-F.HTM", #"results/2003/CB03-M.HTM"
    "results/2004/women.htm", #"results/2004/men.htm"
    "results/2005/CB05-F.htm", #"results/2005/CB05-M.htm"
    "results/2006/women.htm", #"results/2006/men.htm"
    "results/2007/women.htm", #"results/2007/men.htm"
    "results/2008/women.htm", #"results/2008/men.htm"
    "results/2009/09cucb-F.htm", #"results/2009/09cucb-M.htm"
    "results/2010/2010cucb10m-f.htm", #"results/2010/2010cucb10m-m.htm"
    "results/2011/2011cucb10m-f.htm", #"results/2011/2011cucb10m-m.htm"
    "results/2012/2012cucb10m-f.htm" #"results/2012/2012cucb10m-m.htm"
    )

#### Text URLS
urls = paste(ubase, menURLs, sep="")
urls[1:4]
#URLs For Women
urlsWomen <- paste(ubase, womenURLs, sep="")


```

```{r tableExtractFuntion1}
extractResTable =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "male", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    else if (year == 2009 & sex == "male") {
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      div1 = getNodeSet(doc, "//div[@class='Section1']")
      pres = getNodeSet(div1[[1]], "//pre")
      els = sapply(pres, xmlValue)
    }
    else if (year == 1999 & sex == "male") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }




extractResTableWomen =
  #
  # Retrieve data from web site, 
  # find the preformatted text,
  # and write lines or return as a character vector.
  #
  function(url = "http://www.cherryblossom.org/results/2009/09cucb-F.htm",
           year = 1999, sex = "female", file = NULL)
  {
    #added encoding for windows users who get an "A" symbol
    doc = htmlParse(url, encoding="UTF-8")
    print(url)
    if (year == 2000) {
      # Get preformatted text from 4th font element
      # The top file is ill formed so the <pre> search doesn't work.
      ff = getNodeSet(doc, "//font")
      txt = xmlValue(ff[[4]])
      els = strsplit(txt, "\r\n")[[1]]
    }
    else if (year == 2009 & sex == "male") {
      # Get preformatted text from <div class="Section1"> element
      # Each line of results is in a <pre> element
      div1 = getNodeSet(doc, "//div[@class='Section1']")
      pres = getNodeSet(div1[[1]], "//pre")
      els = sapply(pres, xmlValue)
    }
    else if (year == 1999 & sex == "female") { # have to add this else if statement
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\n")[[1]]   
    } 
    else {
      # Get preformatted text from <pre> elements
      pres = getNodeSet(doc, "//pre")
      txt = xmlValue(pres[[1]])
      els = strsplit(txt, "\r\n")[[1]]   
    } 
    
    if (is.null(file)) return(els)
    # Write the lines as a text file.
    writeLines(els, con = file)
  }



```

Code provided by the professor to load the runners data from the URLS. These are raw tables and they still have to be procesed
```{r}

#### Textbook example with (1) URL
df <- extractResTable(url = "http://www.cherryblossom.org/results/2000/Cb003m.htm", year = 2000, sex = "male", file = NULL)

#### Textbook extraction of Male tables (results in an error)
years = 1999:2012
menTables = mapply(extractResTable, url = urls, year = years)
names(menTables) = years
sapply(menTables, length)

urls[1]


#### Modified textbook extraction of Male tables (results in 1999 having (1) record)
menTables = mapply(extractResTable, url = urls, year = years)
names(menTables) = years
sapply(menTables, length)

#### Code to compare and contrast the format of two different years
substr(menTables$'1999', start = 1, stop = 100)
menTables$'2000'[1:10]

#### Corrected function to pull down Male tables with consistent format
menTables = mapply(extractResTable, url = urls, year = years)
names(menTables) = years
sapply(menTables, length)

#### Confirmation that the 1999 and other years have consistent formatting
menTables$'2000'[1:10]
menTables[[2]][1:10]

```
```{r}
#### Save the outputs
save(menTables, file = "/Users/samanthasprague/Desktop/CBMenTextTables.rda")
```


Code to obtain the women tables
```{r}
#### Textbook example with (1) URL

df <- extractResTableWomen(url = "http://www.cherryblossom.org/results/2000/Cb003f.htm", year = 2000, sex = "female", file = NULL)

head(df)
#### Textbook extraction of Male tables (results in an error)
years = 1999:2012

womenTables = mapply(extractResTableWomen, url = urlsWomen, year = years)
names(womenTables) = years
sapply(womenTables, length)

urls[1]


#### Modified textbook extraction of Male tables (results in 1999 having (1) record)
womenTables = mapply(extractResTableWomen, url = urlsWomen, year = years)
names(womenTables) = years
sapply(womenTables, length)

#### Code to compare and contrast the format of two different years
substr(womenTables$'1999', start = 1, stop = 100)
womenTables$'2000'[1:10]

#### Corrected function to pull down Male tables with consistent format
womenTables = mapply(extractResTableWomen, url = urlsWomen, year = years)
names(womenTables) = years
sapply(womenTables, length)

#### Confirmation that the 1999 and other years have consistent formatting
womenTables$'2000'[1:10]
womenTables[['2001']][1:10]
```


```{r}
head(womenTables)
```


Text Function to extract the variables from the above tabels
```{r function2}



### Textbook to select the columns
findColLocs = function(spacerRow) {
spaceLocs = gregexpr(" ", spacerRow)[[1]]
rowLength = nchar(spacerRow)
if (substring(spacerRow, rowLength, rowLength) != " ")
return( c(0, spaceLocs, rowLength + 1))
else return(c(0, spaceLocs))
}


selectCols =
function(colNames, headerRow, searchLocs)
{
sapply(colNames,
function(name, headerRow, searchLocs)
{
startPos = regexpr(name, headerRow)[[1]]
if (startPos == -1)
return( c(NA, NA) )
index = sum(startPos >= searchLocs)
c(searchLocs[index] + 1, searchLocs[index + 1])
},
headerRow = headerRow, searchLocs = searchLocs )
}



extractVariables =
function(file, varNames =c("name", "home", "ag", "gun",
"net", "time"))
{
# Find the index of the row with =s

  eqIndex = grep("^===", file)
if (length(eqIndex) == 0 ) Header=FALSE else Header=TRUE
print(Header)  
# Extract the two key rows and the data
if (Header==TRUE){
        spacerRow = file[eqIndex]
        headerRow = tolower(file[ eqIndex - 1 ])
        body = file[ -(1 : eqIndex) ]
        #print(head(body))
        blanks = grep ("^([[:blank:]]|#[[:blank:]])*$", body)
        
        if (length(blanks) != 0){
          body = body[-blanks]} 
          #print(blanks)
        # Obtain the starting and ending positions of variables
        searchLocs = findColLocs(spacerRow)
        print(searchLocs)
        locCols = selectCols(varNames, headerRow, searchLocs)
        print(locCols)
        Values = mapply(substr, list(body), start = locCols[1, ],
        stop = locCols[2, ])
        colnames(Values) = varNames
        invisible(Values)
  }else{
        firstRec = grep("^[[:blank:]]+1[[:blank:]]+", file)
        #print(firstRec)

        body = file[-(1:firstRec-1)]
        blanks = grep ("^([[:blank:]]|#[[:blank:]])*$", body)
        
        if (length(blanks) != 0){
          body = body[-blanks]} 
          #print(blanks)
        # Obtain the starting and ending positions of variables
        #print(head(body))
        headerRow=tolower("PLACE  NUM   Name                 AG  HOMETOWN            GUN T   NET M")
        spacerRow="===== ===== ==================== === ==================  ======= ======="
                # "    1  6002 Elana MEYER           34 Rep Of S.africa      52:15   52:16#"
        searchLocs = findColLocs(spacerRow)
        print(searchLocs)
        
        locCols = selectCols(varNames, headerRow, searchLocs)
        print(locCols)
        Values = mapply(substr, list(body), start = locCols[1, ],
        stop = locCols[2, ])
        colnames(Values) = varNames
        invisible(Values)
      
    }
}


convertTime = 
  function(timeToSplit){
    timePieces = strsplit(timeToSplit,":")
    timePieces = sapply(timePieces, as.numeric)
    runTime = sapply(timePieces,
                        function(x) {
                          if (length(x) == 2) x[1] + x[2]/60
                            else 60*x[1] + x[2] + x[3]/60
                              })
  return(runTime)
    }

```

```{r CreateMatrix}

menResMat = lapply(menTables, extractVariables)

length(menResMat)
sapply(menResMat, nrow)


```

Results for Women
```{r}
womenResMat = lapply(womenTables, extractVariables)

length(womenResMat)
sapply(womenResMat, nrow)

#womenResMat[['2001']]

```



# Clean and reformat the data (Textbook)
```{r}
## Textbook's starting point to convert age into a numeric value
age = as.numeric(menResMat[['2012']][,'ag'])
tail(age)

age = sapply(menResMat, function(x) as.numeric(x[,'ag']))
#examine age by using a boxplot
boxplot(age,ylab="Age", xlab="Year", main="Male Age Distribution by Year")
```


Get Womens Age
```{r}
## Textbook's starting point to convert age into a numeric value
womenAge = as.numeric(womenResMat[['2001']][,'ag'])
tail(womenAge)

womenAge = sapply(womenResMat, function(x) as.numeric(x[,'ag']))
#examine age by using a boxplot
boxplot(womenAge,ylab="Age", xlab="Year", main="Female Age Distribution by Year")
```





Look into why years 2003 and 2016 are different from the rest.



```{r}
head(menTables[['2000']])
head(menResMat[['2000']])
##### In order to fix the issue a line was modified in the selectCols function:
## to use this line: c(searchLocs[index] + 1, searchLocs[index + 1])
## instrad of c(searchLocs[index] + 1, searchLocs[index + 1] - 1)
```

```{r}
## Check for NA values in the age column
sapply(age, function(x) sum(is.na(x)))
```
```{r}
## Womans Age NA's

sapply(womenAge, function(x) sum(is.na(x)))
```


```{r}
charTime = menResMat[[1]][,'time']
 runTime  <- sapply(charTime, convertTime)
boxplot(runTime)
head(runTime)
charTime
```

Comparison of ages
```{r}

boxplot(age,ylab="Age", xlab="Year")

### Create the dataframe for the Age
s=1

for (i in names(age)) {
  #print(age[[i]])
  age_df_tmp <- as.data.frame(age[[i]])
  age_df_tmp$year <- i
  if (s != 1) {
    age_df <- rbind(age_df_tmp,age_df)
  }else
  { age_df<- age_df_tmp}
  s=2
}
 dim(age_df)

```        


```{r}
### Build Dataframe for WomanAge
#womenAge[['2001']]
s=1

for (i in names(womenAge)) {
  print(i)
  age_df_tmp <- as.data.frame(womenAge[[i]])
  age_df_tmp$year <- i
  if (s != 1) {
    womenAge_df <- rbind(age_df_tmp,womenAge_df)
  }else
  { womenAge_df<- age_df_tmp}
  s=2
}
 dim(womenAge_df)
```

```{r}
library(lattice)
```
        
        
```{r}

### Name columns for Male Age
names(age_df) <- c("age", "year")

head(age_df)
age_df$year <- as.factor(age_df$year)

age_df <- age_df[!is.na(age_df$age),]

summary(age_df)
dim(age_df)

densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)
```

```{r}
## Name The columns for woman age
names(womenAge_df) <- c("age", "year")

head(womenAge_df)
womenAge_df$year <- as.factor(womenAge_df$year)

womenAge_df <- womenAge_df[!is.na(womenAge_df$age),]

summary(womenAge_df)
dim(womenAge_df)

densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE)

```
        
```{r}
### Remove 0 Ages for Men
library(ggplot2)
age_df <- age_df[age_df$age !=0,]
summary(age_df)
densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)
boxplot(age_df, ylab="Age", xlab="Year", main="Male ")

ggplot(data=age_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")


```




```{r}
### Remove 0 Ages for woman
#library(ggplot2)
womenAge_df <- womenAge_df[womenAge_df$age !=0,]
summary(womenAge_df)
densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE)

ggplot(data=womenAge_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")


```


```{r}
library(doBy)
### Summary for Men
summaryBy(age ~ year, data = age_df, 
          FUN = list(mean, max, min, median, sd))

```


```{r}
library(doBy)
### Summary for Women
summaryBy(age ~ year, data = womenAge_df, 
          FUN = list(mean, max, min, median, sd))

```

        
```{r}
### Male Histogram
histogram(age_df$age[age_df$age <20])
#
densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=age_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```

```{r}
### woman Histogram
histogram(womenAge_df$age[womenAge_df$age <20])
#
densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=womenAge_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```


```{r}
### Remove runners < 18 Years Old. 
## https://www.verywellfit.com/age-requirements-for-running-marathons-2911428#targetText=Marathon%20Age%20Requirements,as%2010%20in%20previous%20years.


age_df <- age_df[age_df$age >=18,]
dim(age_df)
summary(age_df)
boxplot(age~year,data=age_df, main="Age by Year",
   xlab="Year", ylab="Age")

densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=age_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```

```{r}
### Remove runners < 18 Years Old. 
## https://www.verywellfit.com/age-requirements-for-running-marathons-2911428#targetText=Marathon%20Age%20Requirements,as%2010%20in%20previous%20years.


womenAge_df <- womenAge_df[womenAge_df$age >=18,]
dim(womenAge_df)
summary(womenAge_df)
boxplot(age~year,data=womenAge_df, main="Age by Year",
   xlab="Year", ylab="Age")

densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=womenAge_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```


```{r}
summaryBy(age ~ year, data = age_df, 
          FUN = list(mean, max, min, median, sd))
```



```{r}
summaryBy(age ~ year, data = womenAge_df, 
          FUN = list(mean, max, min, median, sd))
```



```{r}

age_df <- age_df[age_df$age < 80,]
dim(age_df)
summary(age_df)
boxplot(age~year,data=age_df, main="Age by Year",
   xlab="Year", ylab="Age")


densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=age_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```



```{r}

womenAge_df <- womenAge_df[womenAge_df$age < 80,]
dim(womenAge_df)
summary(womenAge_df)
boxplot(age~year,data=womenAge_df, main="Age by Year",
   xlab="Year", ylab="Age")


densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE)



ggplot(data=womenAge_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")
```



```{r}
summaryBy(age ~ year, data = age_df, 
          FUN = list(mean, max, min, median, sd))
```

```{r}
summaryBy(age ~ year, data = womenAge_df, 
          FUN = list(mean, max, min, median, sd))
```



```{r}
age_df <- age_df[age_df$age <= 70,]
dim(age_df)
summary(age_df)
boxplot(age~year,data=age_df, main="Male Age by Year (Outliers Removed)",
   xlab="Year", ylab="Age")

densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE, main="Male Age Density by Year")

```
```{r}



ggplot(data=age_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+ 
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")+
  guides(fill=FALSE)+
  ggtitle("Male Age Density by Year")
```


```{r}
womenAge_df <- womenAge_df[womenAge_df$age <= 60,]
dim(womenAge_df)
summary(womenAge_df)
boxplot(age~year,data=womenAge_df, main="Female Age by Year (No Outliers)",
   xlab="Year", ylab="Age")

densityplot( ~ age | year, data = womenAge_df,
bw = 0.5, plot.points = FALSE, main="Female Age Density by Year")



ggplot(data=womenAge_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")+
  ggtitle("Female Age Density by Year")
```




```{r}
combined_df <- combined_df[combined_df$age <= 60,]
dim(combined_df)
summary(combined_df)
boxplot(age~year,data=combined_df, main="Age by Year -- All Runners",
   xlab="Year", ylab="Age")

densityplot( ~ age | year, data = combined_df,
bw = 0.5, plot.points = FALSE)


ggplot(data=combined_df, map=aes(x=age)) + 
  geom_density()+
  facet_wrap(~year) +
  geom_vline(aes(xintercept=mean(age), color="red"),
             linetype="dashed")+
  geom_vline(aes(xintercept=median(age), color="blue"),
             linetype="dashed")+
  ggtitle("Age Density by Year for All Runners")

names(combined_df)[4] <- "gender"
names(combined_df)

ggplot(data=combined_df, map=aes(x=age, color=gender)) + 
  geom_density()+
  facet_wrap(~year) +
#  geom_vline(aes(xintercept=mean(age), color="red"),
#             linetype="dashed")+
# geom_vline(aes(xintercept=median(age), color="blue"),
#             linetype="dashed")+
  ggtitle("Age Density by Year and Gender")
```




```{r}

summaryBy(age ~ year, data = age_df, 
          FUN = list(mean, max, min, median, sd))

```


```{r}

summaryBy(age ~ year, data = womenAge_df, 
          FUN = list(mean, max, min, median, sd, nrow))

```
```{r}
summary(womenAge_df)
table(womenAge_df$year)
```

womenAge_df


```{r}
library(sm)

sm.density.compare(age_df$age, age_df$year, xlab="Age")
title(main="Male Age Density")


densityplot( ~ age | year, data = age_df,
bw = 0.5, plot.points = FALSE)

```
        
## Linear regresion
```{r}
### Scatter Plot
ggplot(data = age_df, map=aes(year,age))+
  geom_point()+
  geom_jitter()
```


```{r}
### Scatter Plot
ggplot(data = womenAge_df, map=aes(year,age))+
  geom_point()+
  geom_jitter()
```



```{r}
#create a new variable that contains the year but as a integer
age_df$year2 <- as.numeric(as.character(age_df$year))

### Create the linear regresion

lm_fit <- lm(age ~ year2 , data=age_df)

summary(lm_fit)

```

```{r}
#create a new variable that contains the year but as a integer
womenAge_df$year2 <- as.numeric(as.character(womenAge_df$year))

### Create the linear regresion

lm_fit_w <- lm(age ~ year2 , data=womenAge_df)

summary(lm_fit_w)

```





```{r}
# Plot the residuals
plot(lm_fit)
```


```{r}
# Plot the residuals
plot(lm_fit_w)
```


```{r}
unique(age_df$year2)
### Scatter Plot
ggplot(data = age_df, map=aes(year2,age))+
  geom_point()+
  geom_jitter()+
  geom_smooth(method = "lm", color = "red")

```


```{r}
unique(womenAge_df$year2)
### Scatter Plot
ggplot(data = womenAge_df, map=aes(year2,age))+
  geom_point()+
  geom_jitter()+
  geom_smooth(method = "lm", color = "red")
  ggtitle("Linear Model ")

```



The runeers age difference between the years 1999 and 2012 is about 5 years younger.
```{r}
ggplot(data=age_df[age_df$year=="1999" | age_df$year=="2012",], mapping = aes(sample=age, color=year)) + 
  stat_qq(geom='line', distribution = 'qunif') +
  labs(x="Quantile", y="Age", title="Male Runner's Age Comparison for Years 1999 vs 2012")
```


```{r}
ggplot(data=womenAge_df[womenAge_df$year=="1999" | womenAge_df$year=="2012",], mapping = aes(sample=age, color=year)) + 
  stat_qq(geom='line', distribution = 'qunif') +
  labs(x="Quantile", y="Age", title="Female Runner's Age Comparison for Years 1999 vs 2012")
```
 
 
```{r}
ggplot(data=womenAge_df[womenAge_df$year=="1999" | womenAge_df$year=="2012",], mapping = aes(sample=age, color=year)) + 
  stat_qq(geom='line', distribution = 'qunif') +
  labs(x="Quantile", y="Age", title="Female Runner's Age Comparison for Years 1999 vs 2012")
```


 
```{r}
women1999 = womenAge_df[womenAge_df$year == 1999, "age" ]
women2012 = womenAge_df[womenAge_df$year == 2012, "age" ]

plot(density(women1999, na.rm = TRUE),
     ylim = c(0, 0.08), col = "purple",
     lwd = 3,  xlab = "Age (years)",  main = "")
title(main = "Female Age Density in 1999 vs 2012")
lines(density(women2012, na.rm = TRUE),
      lwd = 3, lty = 2, col="green")
legend("topleft", col = c("purple", "green"), lty= 1:2, lwd = 3,
       legend = c("1999", "2012"), bty = "n")
```
```{r}

womenAge_df$sex <- "female"
age_df$sex <- "male"

combined_df <- rbind(womenAge_df,age_df)

```

```{r}
boxplot(age~year,data=combined_df, main="Age by Year",
   xlab="Year", ylab="Age")
```

```{r}
summary(combined_df)
```

```{r}

combined_df$year2<-as.numeric(as.character(combined_df$year))

lm_fit_comb <- lm(age ~ year2 , data=combined_df)

summary(lm_fit_comb)
```
 
 
 
```{r}
head(combined_df)
```
 
```{r}
lm_fit_comb_sex <- lm(age ~ year2 + sex + year2*sex  , data=combined_df)

summary(lm_fit_comb_sex)
names(combined_df)

plot(combined_df$year2, combined_df$age)
abline(lm_fit_comb_sex)
```
 
 
```{r}
unique(womenAge_df$year2)
### Scatter Plot
ggplot(data = combined_df, map=aes(year2,age))+
  geom_point()+
  geom_jitter()+
  geom_smooth(method = "lm", color = "red")




equation1=function(x){coef(lm_fit_comb_sex)[2]*x+coef(lm_fit_comb_sex)[1]}
equation2=function(x){coef(lm_fit_comb_sex)[2]*x+coef(lm_fit_comb_sex)[1]+coef(lm_fit_comb_sex)[3]}

ggplot(data = combined_df, map=aes(year2,age))+
  geom_point()+
  geom_jitter()+
  geom_smooth(method = "lm", aes(color=sex))+
  ggtitle("Multiple Linear for Female and Male Runners Age")+
  xlab("Year")


ggplot(data = combined_df, map=aes(year2,age))+
  geom_point()+
  geom_jitter()+
  geom_smooth(method = "lm", color="red")+
  ggtitle("Linear for Female and Male Runners Age")+
  xlab("Year")
```
 
 
 
```{r}
plot(lm_fit_comb)
```
 
 
 
```{r}
comb1999 = combined_df[combined_df$year == 1999, "age" ]
comb2012 = combined_df[combined_df$year == 2012, "age" ]

plot(density(comb1999, na.rm = TRUE),
     ylim = c(0, 0.07), col = "purple",
     lwd = 3,  xlab = "Age (years)",  main = "")
title(main = "Combined Male & Female Age Density in 1999 vs 2012")
lines(density(comb2012, na.rm = TRUE),
      lwd = 3, lty = 2, col="green")
legend("topleft", col = c("purple", "green"), lty= 1:2, lwd = 3,
       legend = c("1999", "2012"), bty = "n")
```




 
```{r}
ggplot(data=combined_df[combined_df$year=="1999" | combined_df$year=="2012",], mapping = aes(sample=age, color=year)) + 
  stat_qq(geom='line', distribution = 'qunif') +
  labs(x="Quantile", y="Age", title="Male and Female Runner's Age Comparison for Years 1999 vs 2012")
```

```{r}
i2<-summaryBy(age ~ year, data = combined_df, 
          FUN = list(mean, median))
```


```{r}
library(formattable)
formattable(i2)
```

```{r}

customGreen0 = "#DeF7E9"

customGreen = "#71CA97"

formattable(i2, align =c("l","c","c"), list(
  `year` = formatter("span", style = ~ style(color = "grey",font.weight = "bold")), 
  `age.mean`= color_tile(customGreen, customGreen0),
  `age.median`= color_tile(customGreen, customGreen0)
))
```


```{r}

```


```{r}
i3<-summaryBy(age ~ year, data = age_df, 
          FUN = list(mean, median))

customRed0 = "#FEFEFE"

customRed = "#00A4E4"

formattable(i3, align =c("l","c","c"), list(
  `year` = formatter("span", style = ~ style(color = "black", font.weight = "bold")), 
  `age.mean`= color_tile(customRed, customRed0),
  `age.median`= color_tile(customRed, customRed0)))
```



```{r}
i4<-summaryBy(age ~ year, data = womenAge_df, 
          FUN = list(mean, median))

customRed0 = "#FFFFFF"

customRed = "#E96196"

formattable(i4, align =c("l","c","c"), list(
  `year` = formatter("span", style = ~ style(color = "black", font.weight = "bold")), 
  `age.mean`= color_tile(customRed, customRed0),
  `age.median`= color_tile(customRed, customRed0)))
```

```{r}
i2
```

```{r}
i3
```

