---
title: "Real-Time Location System Case Study"
author: "Eduardo Cantu Medellin, Samantha Sprague, Solange Garcia de Alford"
date: "August 28, 2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Description
The floor plan has 6 fixed access points. The recordings of the signal strenght was done in steps of 45 degrees, a total of 8 recordings per sample. There were 110 samples recorded accross the floor.
# Raw Data
## Loading Data
```{r LoadingData}
#Read the entire document into a string carachter vector rawTxt
rawTxt <- readLines("Data/offline.final.trace.txt")
```
Total number of lines in the text: `r length(rawTxt)`  
Number of lines starting with the '#' symbol: `r sum(substr(rawTxt,1,1) == "#")`
## Procesing Raw Data
```{r dataProc1}
# Splits the line by ';'
strsplit(rawTxt[4],";")[[1]]
```
```{r dataProc2}
# Splits the line by ';' , '=', ',' and store it in a character vector token
tokens=strsplit(rawTxt[4],"[;=,]")[[1]] 
tokens[1:10]
```
Extract values from the tokens, not the field names
```{r dataProc3}
#Extract Data
tokens[c(2,4,6:8,10)]
```
Extract what is left of the tokens data
```{r dataProc4}
#Extract Data
tokens[-(1:10)]
```
Create a matrix with the data then column bind
```{r dataProc5}
tmpMat= matrix(tokens[-(1:10)], ncol=4, byrow = TRUE)
matrix_rec = cbind(matrix(tokens[c(2,4,6:8,10)],nrow=nrow(tmpMat),ncol=6, byrow=TRUE),tmpMat)
matrix_rec
```
Matrix dimensions `r dim(matrix_rec)`
```{r lineProcessFunction}
processLine = function(x){
  tokens=strsplit(x,"[;=,]")[[1]]
  if (length(tokens) == 10)
    return(NULL)
  tmpMat= matrix(tokens[-(1:10)], ncol=4, byrow = TRUE)
  cbind(matrix(tokens[c(2,4,6:8,10)],nrow=nrow(tmpMat),ncol=6, byrow=TRUE),tmpMat)
}
```
Apply the function for the first 16 lines
```{r applyFunction}
tmpRestult = lapply(rawTxt[4:20], processLine)
sapply(tmpRestult,nrow)
```
Bind all the matrices on tmpResult
```{r BindMatrix}

offlineData <- as.data.frame(do.call("rbind",tmpRestult))
#offlineData
```
```{r processAllData}
# Get the number of lines that do not start with '#'
options(error = recover, warn=2)
linesToProcess <- rawTxt[ substr(rawTxt,1,1) != "#"]
tmpRestult = lapply(linesToProcess, processLine)
#Append final data
offlineData <- as.data.frame(do.call("rbind",tmpRestult))

head(offlineData)
```
Total number of measurments: `r dim(offlineData)`
## Cleaning the Data
```{r dataCleaning}
#Name the columns of the dataset
names(offlineData) <- c("time","scanMac","posX","posY","posZ","orientation"
                        ,"mac","signal", "channel","type")
head(offlineData)
```
```{r setVariablesType}
# set the variable types
numericVar <- c("time", "posX","posY","posZ","orientation","signal")
offlineData[,numericVar] <- as.data.frame(apply(offlineData[,numericVar],2, as.numeric))
head(offlineData)
#unique(offlineData$mac)
```
The analysis will only use data from the "access points", therefore all records that are not coming from an access point will be deleted.
```{r deleteNonAccessPointRec}
#Keep only the access points records
offlineData <- offlineData[offlineData$type == "3",]
#remove the 'type' field from the dataset after removing all non access points records
offlineData <- offlineData[, "type" != names(offlineData)]
head(offlineData)
```
New dimension after removing the column and non-access-point records: `r dim(offlineData)`
Time variable. To use the POSIXt format we need to use the time in seconds not milliseconds. Convert the time variable to seconds by dividing by 1000 the milliseconds.
```{r timeFormat}
offlineData$rawTime <-  offlineData$time
offlineData$time <- offlineData$rawTime / 1000
class(offlineData$time) = c("POSIXt", "POSIXct")
summary(offlineData[,numericVar])
```
```{r summaryForFactors}
offlineData$mac <- as.character(offlineData$mac)
summary(offlineData[,c("mac","channel","scanMac")])
summary(offlineData[,c("mac","channel")])
```
There are two fields where their infomration is the same accross all the rows or observations. These fields 'posZ' and 'scanMac' can be removed from the data set
```{r removeCol}
# keep the fields with information
offlineData <- offlineData[, !(names(offlineData) %in% c("scanMac","posZ"))]
head(offlineData)
```
### Orientation Field
The dataset should only contain 8 values for orientation, i.e., 0,45,90,..,315
```{r orientationCheck}
length(unique(offlineData$orientation))
plot(ecdf(offlineData$orientation), ylab="Empirical CDF", xlab="Orientation", main="")
```
```{r orientationFunction}
roundOrientation <- function(angles){
  refs = seq(0, by = 45, length = 9)
  q = sapply(angles, function(o) which.min(abs(o-refs)))
  c(refs[1:8],0)[q]
}
```
```{r addAngles}
#add the angles field by using the function
offlineData$angle <- roundOrientation(offlineData$orientation)
```
```{r chartAngles}
with(offlineData,boxplot(orientation ~ angle,
                         xlab= "nearest 45 degree angle",
                         ylab= "orientation"))
```
### MAC Addresses
```{r macAddressNumbers}
c(length(unique(offlineData$mac)), length(unique(offlineData$channel)))
sort(table(offlineData$mac), decreasing = TRUE)
offlineData[offlineData$mac == "02:42:1c:4e:b5:c0",]
```
```{r keepTopSevenMacs}
subMacs <-  names(sort(table(offlineData$mac), decreasing=TRUE))[1:7]
subMacs
offlineData <- offlineData[offlineData$mac %in% subMacs,]
unique(offlineData$mac)
table(offlineData$mac)
#offlineData[offlineData$mac %in% subMacs,]
#head(offlineData)
#c(length(unique(offlineData$mac)), length(unique(offlineData$channel)))
```
## Exploring Hand held position
```{r handHeldExploration}
locDF <- with(offlineData,
              by (offlineData, list(posX,posY), function(x) x))
length(locDF)
#empty combinations of (x,y)
sum(sapply(locDF,is.null))
```
```{r dropNullCombinations}
locDF <- locDF[ !sapply(locDF, is.null)]
length(locDF)
locDF[[5]]
```
```{r locCounts}
#number of observations per location
locCounts <- sapply(locDF, nrow)
#or we can do this instead
locCounts <- sapply(locDF, 
                    function(df)
                      c(df[1,c("posX","posY")], count = nrow(df)))
class(locCounts)
dim(locCounts)
locCounts[,1:15]
```
```{r plotCounts}
locCounts = t(locCounts)
plot(locCounts, type = "n", xlab="",ylab="")
text(locCounts, labels = locCounts[,3], cex = .8, srt = 45)
```
## Signal Strength
```{r pltoSignalS}

library(lattice)

bwplot(signal ~ factor(angle) | mac , data = offlineData,
       subset = posX == 2 & posY == 12
       & mac != "00:0f:a3:39:dd:cd",
       layout = c(2,3))

```
```{r densityPlots}


densityplot( ~ signal | mac + factor(angle), data = offlineData,
subset = posX == 24 & posY == 4 &
mac != "00:0f:a3:39:dd:cd",
bw = 0.5, plot.points = FALSE)



```
```{r}



offlineData$posXY <- paste (offlineData$posX,offlineData$posY, sep = "-")

byLocAngleAp <-  with(offlineData,
                      by(offlineData,list(posXY,angle,mac),
                         function(x) x))

signalSummary = lapply(byLocAngleAp,
                       function(oneLoc){
                         ans = oneLoc[1,]
                         ans$medSignal = median(oneLoc$signal)
                         ans$avgSignal = mean(oneLoc$signal)
                         ans$num = length(oneLoc$signal)
                         ans$sdSignal = sd(oneLoc$signal)
                         ans$iqrSignal = IQR(oneLoc$signal)
                         ans
                       })

offlineSummary = do.call("rbind",signalSummary)


breaks = seq(-90, -30, by = 5)

head(offlineData$posXY)
head(byLocAngleAp)

#bwplot(sdSignal ~ cut(avgSignal, breaks = breaks),
#data = offlineSummary,
#subset = mac != "00:0f:a3:39:e1:c0",
#xlab = "Mean Signal", ylab = "SD Signal")
```
## Relation between Signal and Distance
```{r examineAndTestDistance}
#Get one AP and one angle 



oneAPAngle <- subset(offlineSummary, mac==subMacs[5] & angle ==  0)

library(fields)
smoothSS <- Tps(oneAPAngle[,c("posX","posY")], oneAPAngle$avgSignal)
vizSmooth <- predictSurface(smoothSS)
plot.surface(vizSmooth,type = "C", main=subMacs[5])
points(oneAPAngle$posX, oneAPAngle$posY, pch=19, cex = 0.5)



```
Wraping the previous code into a surfaceSS function
```{r surfaceSSFunction}
surfaceSS = function (m, a, d){
  oneAPAngle <- subset(d, mac == m & angle == a)
  smoothSS <- Tps(oneAPAngle[,c("posX","posY")], oneAPAngle$avgSignal)
  vizSmooth <- predictSurface(smoothSS)
  plot.surface(vizSmooth,type = "C", main=paste("AP: ",m,"Angle:",a))
  points(oneAPAngle$posX, oneAPAngle$posY, pch=19, cex = 0.5)
}



```



```{r ContinuationSSMultiple}
parcur <- par(mfrow=c(7,3), mar = rep(1,4))
mapply(surfaceSS,m = subMacs[ rep(c(1,2,3,4,5,6,7), each=3)], 
       a= rep(c(0,90,135), each=1),
       d = list(data=offlineSummary))
#rep(c(0,135),2)
```
Use the previous chart to define the X and Y positions for the APs using the floor plan
```{r}
#Create the matrix with the X and Y Positions for all the APs

AP = matrix( c( 7.5, 6.3, 6.5, 7.6, 2.5, -.8, 12.8, -2.8,
1, 14, 33.5, 9.3, 33.5, 2.8),
ncol = 2, byrow = TRUE,
dimnames = list(subMacs, c("x", "y") ))
diffs <- offlineSummary[,c("posX","posY")] - AP[offlineSummary$mac,]
offlineSummary$dist <-  sqrt(diffs[,1]^2 + diffs[,2]^2)
xyplot(signal~dist | factor(mac) + factor(angle), data=offlineSummary, pch =19, cex =0.3,xlab="Distance")



```
####
####  SAMANTHA & SOLANGE SECTIONS - 
###      1. UPLOAD ONLINE DATA
###      2. CLEAN AND PREPARE ONLINE DATA
###      3. IDENTIFY SUBSETS - ONLINE AND OFFLINE DATA (TRAIN DATA)
###      4. IDENTIFY NEAREST NEIGHBORS
###      5. PREDICTION - tbd
###


```{r}



online <- readLines("Data/online.final.trace.txt")

#rawTxt <- readLines("Data/offline.final.trace.txt")

```



```{r}

tokens=strsplit(online[4],"[;=,]")[[1]]
tokens[1:10]
tokens[c(2,4,6:8,10)]

tokens[-(1:10)]

tmpMat= matrix(tokens[-(1:10)], ncol=4, byrow = TRUE)

matrix_rec = cbind(matrix(tokens[c(2,4,6:8,10)],nrow=nrow(tmpMat),ncol=6, byrow=TRUE),tmpMat)



```

```{r}

processLine = function(x){
  tokens=strsplit(x,"[;=,]")[[1]]
  if (length(tokens) == 10)
    return(NULL)
  tmpMat= matrix(tokens[-(1:10)], ncol=4, byrow = TRUE)
  cbind(matrix(tokens[c(2,4,6:8,10)],nrow=nrow(tmpMat),ncol=6, byrow=TRUE),tmpMat)
  
}


```



```{r processAllData}

# Get the number of lines that do not start with '#'

options(error = recover, warn=2)

linesToProcess <- online[ substr(online,1,1) != "#"]


#Apply processLine function to all lines
tmpResult_on = lapply(linesToProcess, processLine)


#Append final data
onlineData <- as.data.frame(do.call("rbind",tmpResult_on))

head(onlineData)



```

## Cleaning the Data
```{r dataCleaning}


#Name the columns of the dataset onlineData

names(onlineData) <- c("time","scanMac","posX","posY","posZ","orientation"
                        ,"mac","signal", "channel","type")
head(onlineData)

```


```{r setVariablesType}

# set the variable types - mac address is changed to character in onlineData structure

onlineData$mac <- as.character(onlineData$mac)

numericVar <- c("time", "posX","posY","posZ","orientation","signal")

onlineData[,numericVar] <- as.data.frame(apply(onlineData[,numericVar],2, as.numeric))

head(onlineData)

unique(onlineData$mac)

str(onlineData)
nrow(onlineData)

```
The 'remMacAddress' variable will have the mac address that needs to be removed from both offline and online data
```{r}

# This is the mac address to remove.
remMacAddress = "All"



```



```{r}

## Need to eliminate records in onlineData that have least number of observations for the Sub mac addresses 


subMacs_on <-  names(sort(table(onlineData$mac), decreasing=TRUE))[1:7]
head(subMacs_on)


# Remove one mac address
# Per the case study project rubric:  "... and the decision was made to keep the access point with MAC address 00:0f:a3:39:e1:c0 and to eliminate the data corresponding to MAC address 00:0f:a3:39:dd:cd. 

subMacs_on <- subMacs_on[subMacs_on != remMacAddress]
table(subMacs_on)


## Subset of online data with only 7 mac addresses:


onlineData_Sub <- onlineData[onlineData$mac %in% subMacs_on,]

head(onlineData_Sub)

unique(onlineData_Sub$mac)

table(onlineData_Sub$mac)


```

```{r}

# creating the unique location identifiers in the onlineData_Sub data set


onlineData_Sub$posXY = paste(onlineData_Sub$posX, onlineData_Sub$posY, sep = "-")

head(onlineData_Sub)

length(unique(onlineData_Sub$posXY))


```



```{r addAngles}


#add the angles column by using roundOrientation function

onlineData_Sub$angle <- roundOrientation(onlineData_Sub$orientation)

onlineData_Sub

```


```{r}


#Tally the number of signal strengths recorded at each location - Table - angle vs posYX

tabonlineXYA = table(onlineData_Sub$posXY, onlineData_Sub$angle)

tabonlineXYA[1:8, ]

 ##"00:0f:a3:39:dd:cd"
 
```




```{r}
#Change data structure and summarize each mac address with average of signal strengths 

keepVars = c("posXY", "posX","posY", "orientation", "angle")

byLoc = with(onlineData_Sub, by(onlineData_Sub, list(posXY),
                                function(x) {
                                
                                ans = x[1, keepVars]
                                avgSS = tapply(x$signal, x$mac, mean)
                                y = matrix(
                                avgSS,
                                nrow = 1,
                                ncol = 7,
                                dimnames = list(ans$posXY, names(avgSS)))
                                cbind(ans, y)
                                }))


onlineSummary = do.call("rbind", byLoc)

dim(onlineSummary)
names(onlineSummary)

```



```{r}
#Online data new summary structure with signal strength averages by mac address

onlineSummary


```

Here we remove the mac address for the Offline data.
```{r}
# Remove 7th mac from offline data set



subMacs_off <-  names(sort(table(offlineSummary$mac), decreasing=TRUE))[1:7]
subMacs_off <-  subMacs_off[subMacs_off != remMacAddress]

table(subMacs_off)


offlineSum <- offlineSummary[offlineSummary$mac %in% subMacs_off,]

# offlineSum is the variable to use that does not contain the AP above.
```


```{r}

#Creating data structure similar to onlineSummary with a helper function called reshapeSS

reshapeSS = function(data, varSignal = "signal", keepVars = c("posXY", "posX", "posY", "orientation", "angle")) {
byLocation =
with(data, by(data, list(posXY),
function(x) {
ans = x[1, keepVars]
avgSS = tapply(x[ , varSignal ], x$mac, mean)
y = matrix(avgSS, nrow = 1, ncol = 7,
dimnames = list(ans$posXY,
names(avgSS)))
cbind(ans, y)
}))
newDataSS = do.call("rbind", byLocation)
return(newDataSS)
}



```




```{r}

#train reshapeSS

reshapeSStrain = function(data, varSignal = "signal", keepVars = c("posXY", "posX", "posY")) {
byLocation = with(data, by(data, list(posXY),
      function(x) {
      ans = x[1, keepVars]
      avgSS = tapply(x[ , varSignal ], x$mac, mean)
      y = matrix(avgSS, nrow = 1, ncol = 7,
      dimnames = list(ans$posXY,
      names(avgSS)))
      cbind(ans, y)
      }))
newDataSS = do.call("rbind", byLocation)
return(newDataSS)
}



```


```{r}
## The function includes the seletion of the angles.


selectTrain = function(angleNewObs, signals, m)

{
  refs = seq(0, by = 45, length = 8)
  nearestAngle = roundOrientation(angleNewObs)

  if (m %% 2 == 1) {
    angles = seq(-45 * (m - 1) / 2, 45 * (m - 1) / 2, length = m)
  } else {
    m = m + 1
    angles = seq(-45 * (m - 1) / 2, 45 * (m - 1) / 2, length = m)
  if (sign(angleNewObs - nearestAngle) > -1)
    angles = angles[-1]
  else
    angles = angles[-m]
  }
  #print(angles)
  angles = nearestAngle + angles
  angles[angles < 0] = angles[angles < 0] + 360
  angles[angles > 360] = angles[angles > 360] - 360
  angles = sort(angles)
  #print(angles)
  offlineSubset = signals[signals$angle %in% angles,]
  
  trainSS = reshapeSStrain(offlineSubset, varSignal = "avgSignal")
  
 return(trainSS)}



```


```{r}

#Test if the selectTrain function works for all angles. 
train130 = selectTrain(90, offlineSum, m = 3)


```


```{r}

#Find nearest neighbors

findNN = function(newSignal, trainSubset) {
  diffs = apply(trainSubset[ , 4:10], 1,
    function(x) x - newSignal)
  dists = apply(diffs, 2, function(x) sqrt(sum(x^2)) )
  closest = order(dists)
  return(trainSubset[closest, 1:3 ])
}

```



```{r}

#Find nearest neighbors

findwNN = function(newSignal, trainSubset) {
diffs = apply(trainSubset[ , 4:10], 1,
  function(x) x - newSignal)
dists = apply(diffs, 2, function(x) sqrt(sum(x^2)) )
invdists = apply(diffs, 2, function(x) 1/sqrt(sum(x^2)) )
wDistSum=sum(invdists)
#print(invdists)
wDist =invdists/wDistSum
#print(wDistSum)
closest = order(dists)
#print(closest)
return(list(trainSubset[closest, 1:3 ], invdists[order(wDist, decreasing = TRUE)]))
}

```

```{r}

#this Uses Regular Distance


predXY = function(newSignals, newAngles, trainData,
  numAngles = 1, k = 3){
  closeXY = list(length = nrow(newSignals))
  
  for (i in 1:nrow(newSignals)) {
    #print(newAngles[i])
     trainSS = selectTrain(newAngles[i], trainData, m = numAngles)
   
    closeXY[[i]] =
      findNN(newSignal = as.numeric(newSignals[i, ]), trainSS)
    
    
  }
    estXY = lapply(closeXY, function(x) sapply(x[ , 2:3],
                                        function(x) mean(x[1:k])))
  estXY = do.call("rbind", estXY)
  return(estXY)
}


```

```{r}

#this Uses Weighted Distance


predWXY = function(newSignals, newAngles, trainData,
  numAngles = 1, k = 3){
  closeXY = list(length = nrow(newSignals))
  invDist = list(length = nrow(newSignals))
  
  for (i in 1:nrow(newSignals)) {
    #print(newAngles[i])
     trainSS = selectTrain(newAngles[i], trainData, m = numAngles)
   
    closeXY[[i]] =
      findwNN(newSignal = as.numeric(newSignals[i, ]), trainSS)[[1]]
    invDist[[i]] =
      findwNN(newSignal = as.numeric(newSignals[i, ]), trainSS)[[2]]
    
    
    
  }
  
  #print(invDist)
  
  #calcuate the Distance Weight for the Top K N
  distWList = list(length = length(invDist))
  for (i in 1:length(invDist)){
    
    distWeight = list(length=k)
    for (j in 1:k) {
      distWeight[j]=invDist[[i]][j] /sum(invDist[[i]][1:k])
    }
    distWList[[i]]=distWeight
  }
   #print(distWList)
  wXYFactor = list(length(closeXY))
  
  #multiply the weights
  
  for (i in 1:length(closeXY)){
    wXYFactor[[i]]=as.matrix(closeXY[[i]][1:k,2:3] * unlist(distWList[[i]]))
  }
  #print(wXYFactor)
   
  estXY = lapply(wXYFactor, function(x) apply(x, 2,
                                    function(x) sum(x)))
  estXY = do.call("rbind", estXY)
  return(estXY)
}


```



```{r}

## Error Cacluation Function

calcError =
function(estXY, actualXY)
sum( rowSums( (estXY - actualXY)^2) )

```





```{r}

v = 11
permuteLocs = sample(unique(offlineSum$posXY))
permuteLocs = matrix(permuteLocs, ncol = v,
nrow = floor(length(permuteLocs)/v))


#permuteLocs2 = sample(unique((onlineSummary$posXY)))
#permuteLocs2 = matrix(permuteLocs2, ncol = v,
#nrow = floor(length(permuteLocs2)/v))

#permuteLocs


```





```{r}


reshapeSS = function(data,  varSignal = "signal", keepVars = c("posXY", "posX","posY", "orientation", "angle"), sampleAngle = FALSE) {
  refs = seq(0, by = 45, length = 8)
  byLocation = with(data, by(data, list(posXY),
              function(x) {
                    if (sampleAngle) x = x[x$angle == sample(refs, size = 1), ]
                      ans = x[1, keepVars]
                      avgSS = tapply(x[ , varSignal ], x$mac, mean)
                      y = matrix(avgSS, nrow = 1, ncol = 7,
                      dimnames = list(ans$posXY, names(avgSS)))
                      cbind(ans, y)
              }))
newDataSS = do.call("rbind", byLocation)
return(newDataSS)
}

```


This sets the simulated online data using the offline data.
```{r}

onlineCVSummary = reshapeSS(offlineSum, keepVars = keepVars,
                      sampleAngle = TRUE)



```




## This code does not include the 00:0f:a3:39:dd:cd mac address.

This XY Calculation uses relgular distances
```{r}

## This code does not include the 00:0f:a3:39:dd:cd mac address 

K = 20 
err = rep(0, K)

dim(permuteLocs)

for (j in 1:v) { 
  onlineFold  = subset(onlineCVSummary,  posXY %in% permuteLocs[ , j]) 
  offlineFold = subset(offlineSum, posXY %in% permuteLocs[ , -j]) 
  actualFold = onlineFold[ , c("posX", "posY")]
  for (k in 1:K) { 
    estFold = predXY(newSignals = onlineFold[ , 6:12], 
                     newAngles = onlineFold[ , 5], 
                     offlineFold, numAngles = 3, k = k) 
    err[k] = err[k] + calcError(estFold, actualFold) 
    }
}

```
### Plot of the SSE for the Cross Validataion 
```{r}
MinErr=min(err)
minK=which(err==MinErr)[1]
plot(err, type="l", xlab = "K value (#Nbrs) \n All Top AP included", ylab ="Cross Validation Error")
title("Error Values for k values from 1 to 20 Unweighted Scenario")

text(x = minK - 2, y = MinErr + 40, 
     label = as.character(round(MinErr)), col = grey(0.4))
err
```

This XY Calculation uses Weighted distances
```{r}

## This code does not include the 00:0f:a3:39:dd:cd mac address 

K = 20 
errW = rep(0, K)

dim(permuteLocs)

for (j in 1:v) { 
  onlineFold  = subset(onlineCVSummary,  posXY %in% permuteLocs[ , j]) 
  offlineFold = subset(offlineSum, posXY %in% permuteLocs[ , -j]) 
  actualFold = onlineFold[ , c("posX", "posY")]
  for (k in 1:K) { 
    estFold = predWXY(newSignals = onlineFold[ , 6:12], 
                     newAngles = onlineFold[ , 5], 
                     offlineFold, numAngles = 3, k = k) 
    errW[k] = errW[k] + calcError(estFold, actualFold) 
    }
}

```
### Plot of the SSE for the Cross Validataion 
```{r}
MinErr=min(errW)
minK=which(errW==MinErr)[1]
plot(errW, type="l", xlab = "K value (#Nbrs) \n All Top AP included", ylab ="Cross Validation Error")
title("Error Values for k values from 1 to 20 weighted Scenario")
text(x = minK - 2, y = MinErr + 40, 
     label = as.character(round(MinErr)), col = grey(0.4))
err

```
```



